---
title: "Simple PM example, evaluating fit"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{evaluate_fit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


```


Data for this lesson can be downloaded from

https://www.dropbox.com/sh/g21k7hmj69h30y2/AACXkTIJBZVYkrA3adiE6gh1a?dl=0

Loads in data from sampling vignette. Uses
predict() method to get posterior predictions
and summarise_fit function to get summaries of 
these predictions in terms of response proportions
and RTs. 

```{r load}
library(PMDC)

fpath <- system.file("extdata", "fit1.RData", package="PMDC")
load(fpath)

fpath <- system.file("extdata", "fit_multi_1.RData", package="PMDC")
load(fpath)

fpath <- system.file("extdata", "fit_multi_hierarchical_1.RData", package="PMDC")
load(fpath)

theme_simple <- function (base_size = 12, base_family = "") {
  theme_grey(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.background = element_rect(fill="white"),
      panel.grid.minor.y = element_blank(),
      legend.key = element_rect(fill="white", colour= "white"),
      strip.background = element_rect(fill="white"))
}

theme_set(theme_simple())


```

For a quick fit workup just call plot() on fit summaries

```{r plot}

test <- predict(fit)
fit_summaries <- summarise_fit(test, facs="S")

plot(fit_summaries)

```

Can also separately plot fits to response proportions and RTs
```{r plotRP}

plot_RP(fit_summaries, xaxis="S")

```
```{r plotRT}

plot_RT(fit_summaries, xaxis="S")

```

Sometimes response accuracy is preferable to response prportion. 
This can be plotted with plot_RA
```{r plotRA}

plot_RA(fit_summaries, xaxis="S")

```

The methods also work for lists of fits to multiple participants
and for hyper fits
```{r plot_many}


fpath <- system.file("extdata", "fit_multi_1.RData", package="PMDC")
load(fpath)

test <- predict(fit_multi)

fit_summaries <- summarise_fit(test, facs=c("S"))

plot(fit_summaries)
```

```{r plot_h}


test<- predict(fit_multi_hierarchical)

plot(summarise_fit(test, facs=c("S", "cond")))

```
