---
title: "Simple PM example, evaluating samples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{evaluate_samples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


```

Data for this lesson can be downloaded from

https://www.dropbox.com/sh/g21k7hmj69h30y2/AACXkTIJBZVYkrA3adiE6gh1a?dl=0

Loads in data from sampling vignette. Uses
get_post_cred method to get posterior medians 
and credible intervals.

```{r load}
library(PMDC)
library(ggplot2)

fpath <- system.file("extdata", "fit1.RData", package="PMDC")
load(fpath)

fpath <- system.file("extdata", "fit_multi_1.RData", package="PMDC")
load(fpath)

fpath <- system.file("extdata", "fit_multi_hierarchical_1.RData", package="PMDC")
load(fpath)

theme_simple <- function (base_size = 12, base_family = "") {
  theme_grey(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.background = element_rect(fill="white"),
      panel.grid.minor.y = element_blank(),
      legend.key = element_rect(fill="white", colour= "white"),
      strip.background = element_rect(fill="white"))
}

theme_set(theme_simple())


```

An example of how the credible intervals
for parameter values might be plotted. In this case 
the values of 'B' which correspond to response threhsolds.

```{r plot}

post_creds <- get_post_cred(fit)


Bs <- post_creds[grep ("B", rownames(post_creds)),]
## new thing make a data fram efor ggplot
Bs$PM <- NA; Bs$R <- NA
Bs$PM[grep ("C", rownames(Bs))] <- 
  "C"
Bs$PM[grep ("F", rownames(Bs))] <- 
  "F"
Bs$PM[grep ("H", rownames(Bs))] <- "H"

Bs$R[grep ("N", rownames(Bs))] <- "N"
Bs$R[grep ("W", rownames(Bs))] <- "W"
Bs$R[grep ("P", rownames(Bs))] <- "P"


ggplot(Bs, aes(factor(R),q50)) + 
  geom_point(stat = "identity",aes(shape=PM), size=3) +
  geom_errorbar(aes(ymax = q97.5, ymin = q2.5, width = 0.2)) +
  xlab("Session") + ylab("Threshold") +
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line()
  )+geom_line(aes(group=PM, y=q50), linetype=2) 


```


same thing for many subjects
```{r plot_many}


post_creds <- get_post_cred(fit_multi)

Bs <- post_creds[grep ("B", rownames(post_creds)),]
## new thing make a data fram efor ggplot
Bs$PM <- NA; Bs$R <- NA
Bs$PM[grep ("C", rownames(Bs))] <- 
  "C"
Bs$PM[grep ("F", rownames(Bs))] <- 
  "F"
Bs$PM[grep ("H", rownames(Bs))] <- "H"

Bs$R[grep ("N", rownames(Bs))] <- "N"
Bs$R[grep ("W", rownames(Bs))] <- "W"
Bs$R[grep ("P", rownames(Bs))] <- "P"


ggplot(Bs, aes(factor(R),q50)) + 
  geom_point(stat = "identity",aes(shape=PM), size=3) +
  geom_errorbar(aes(ymax = q97.5, ymin = q2.5, width = 0.2)) +
  xlab("Session") + ylab("Threshold") +
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line()
  )+geom_line(aes(group=PM, y=q50), linetype=2) 


```


same thing with hierarchical
```{r plot_hierarchical}



post_creds <- get_post_cred(fit_multi_hierarchical)

Bs <- post_creds[grep ("B", rownames(post_creds)),]
## new thing make a data fram efor ggplot
Bs$PM <- NA; Bs$R <- NA
Bs$PM[grep ("C", rownames(Bs))] <- 
  "C"
Bs$PM[grep ("F", rownames(Bs))] <- 
  "F"
Bs$PM[grep ("H", rownames(Bs))] <- "H"

Bs$R[grep ("N", rownames(Bs))] <- "N"
Bs$R[grep ("W", rownames(Bs))] <- "W"
Bs$R[grep ("P", rownames(Bs))] <- "P"


ggplot(Bs, aes(factor(R),q50)) + 
  geom_point(stat = "identity",aes(shape=PM), size=3) +
  geom_errorbar(aes(ymax = q97.5, ymin = q2.5, width = 0.2)) +
  xlab("Session") + ylab("Threshold") +
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line()
  )+geom_line(aes(group=PM, y=q50), linetype=2) 


```


```{r post_ps}

PMDC::summarise_effect(fit, fun=function(x) x["B.H.W"] - x["B.C.W"])

```

```{r post_ps_multi}

PMDC::summarise_effect(fit_multi, fun=function(x) x["B.H.W"] - x["B.C.W"])

```

```{r post_ps_h}

PMDC::summarise_effect(fit_multi_hierarchical, fun=function(x) x["B.H.W"])

```
TODO: Inference functions for hyper priors