---
title: "Simple PM example, creating model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{setup_sampling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


```

This vignette runs through an example of how to fit the 
Prospective Memory Decision Control (PMDC) model to a single experimental subject's data. 
The experimental 
design is based on Strickland et al. (2018).

In many ways, modelling PM experiments is not too different
to modelling other experiments with the ggdmc software. 
In 'control' conditions, this was the only
task participants performed. Similar to many prospective memory (PM) experiments, 
the experiment included an ongoing task in which participants
made decisions about whether strings of letters were words 
or non-words. These conditions can be modelled
with two racing LBA accumulators, one for word and one for non-word. 
However, the experiment included two conditions with additional PM tasks, which
require some adjustments to model.
The PM task was to submit an alternative
response to certain words in the task. In 'focal' PM conditions,
participants were required to make this alternative response
to one particular PM target word (e.g., press 'j' if you see the word 'giraffe'). In 'non-focal' conditions,
they were required to make this response to any word
within a PM target category (e.g., press 'j' if you see any word that is an animal'). 
Both of the above PM conditions require three accumulators to model. Thus,
the model fitting procedure needs to swap between 2 and three accumulator
architectures. In addition, the model specification required not fully crossing
two factor levels- stimulus type, and PM condition, as there were no PM stimuli
in control blocks of trials.

#### Building a model

Note that the non-focal level is labelled H (for hard), rather than NF. This is
because model.dmc relies on string matching to create the models, and this
string matching assumes that no factor levels will contain a complete substring
of other factor levels.

S: Stimulus type - levels = non-word (n), word(w), PM (p)
R: response levels - Nonword response (N), word response (W), PM response (P)

Although the levels of S and R are the same letters, they are ok, because
one is upper case and the other lower case.

The PM models often needs a custom "match.map".
In prospective memory paradigms PM 'false alarms',
in which participants make a PM response on a non-PM trial, are very rare,
and thus associated rate parameter estimates are not constrained by much data.
Thus, it is a good idea to pool those rates into one PM false alarm parameter
(fa).

When using match.map on a non-factorial design, all
cells of the maps need to be filled with something- even  cells that never
occur in the design. In this design, PM trials and PM responses never occur
under control conditions. That is, the stimulus type factor (word trial
non-word trial, PM trial) is non-factorial, with 3 levels in focal (F) and
non-focal (H), but only 2 levels in control (C). Simililarly, the accumulator
factor (word, non-word, PM) is non-factorial with 2 levels in control but
3 in focal and non-focal. However, all factorial combinations of
design levels need to be filled with something. In order to get around this,
create a dummy parameter for these cells. In this example, the
dummy parameter is  "FAKERATE". This parameter is assigned to the cells,
but never estimated from the data.

```{r map}
library(PMDC)

FR <- list(S = c("n","w","p"), cond=c("C","F", "H"), R=c("N", "W", "P"))
lev <- c("CnN","CwN", "CnW","CwW",
         "FnN","FwN","FpN", "FnW","FwW","FpW", "fa","FpP",
         "HnN","HwN","HpN", "HnW","HwW","HpW", "HpP",
         "FAKERATE")
map_mean_v <- ggdmc:::MakeEmptyMap(FR, lev)
map_mean_v[1:27] <- c(
  "CnN","CwN","FAKERATE", "FnN","FwN","FpN", "HnN","HwN","HpN",
  "CnW","CwW","FAKERATE", "FnW","FwW","FpW", "HnW","HwW","HpW",
  "FAKERATE","FAKERATE","FAKERATE", "fa","fa","FpP", "fa","fa","HpP")

```


In this semi-factorial design, the is no PM accumulator under control
conditions. In order for model.dmc to know this, the user should do two things:
1: input an 'N' argument corresponding to the number of accumulators for
each condition. Specify the number in constants.
2: set the thresholds to 'Inf' for non-existent accumulators.
In addition, set the dummy parameters "FAKERATE" to a constant.


```{r buildmodel}
model0 <- BuildModel(
  p.map     = list(A = "1", B = c("cond", "R"), t0 = "1", mean_v = c("MAPMV"),
                   sd_v = "1", st0 = "1", N = "cond"),
  match.map = list(M = list(n = "N", w = "W", p = "P"), MAPMV = map_mean_v),
  factors   = list(S = c("n","w","p"), cond = c("C","F", "H")),
  constants = c(N.C = 2, N.F = 3, N.H = 3, st0 = 0, B.C.P = Inf,
                mean_v.FAKERATE = 1, sd_v = 1),
  responses = c("N", "W", "P"),
  type      = "norm")

npar <- length(GetPNames(model0))

```

A vector of 'true' values we will simulate from - similar to Strickland et al. (2018)

```{r sim_p_vector}
sim.p.vector <- c(A = .3, B.C.N = 1.3,  B.F.N = 1.3,  B.H.N = 1.3,
              B.C.W = 1.3,  B.F.W = 1.4,  B.H.W = 1.5,
              B.F.P = 1.1,  B.H.P = 1.3,

              t0=.1,

              mean_v.CnN = 2.8,  mean_v.CwN = -0.3, mean_v.CnW=-1,
              mean_v.CwW = 2.9,  mean_v.FnN = 2.8,  mean_v.FwN=-.3,

              mean_v.FpN = -1.6, mean_v.FnW = -1,   mean_v.FwW = 2.9,
              mean_v.FpW = .5 ,  mean_v.fa = -2.4,  mean_v.FpP = 2.5,

              mean_v.HnN = 2.8, mean_v.HwN = -.5,   mean_v.HpN = -.6,
              mean_v.HnW = -.7, mean_v.HwW = 3.0,   mean_v.HpW = 1.6,
              mean_v.HpP = 2.3)

```
              
A naive PM prior(similar to the study):
uniform distribution for t0,
truncated normals, truncated normal for A (0, 10),
truncated normals for Bs (inf), normals for vs.              


```{r set_prior}
prior.p.mean <- c(A = 1, B.C.N = 1,  B.F.N = 1,  B.H.N = 1,
              B.C.W = 1,  B.F.W = 1,  B.H.W = 1,
              B.F.P = 1,  B.H.P = 1,
              
              t0=.3,
              
              mean_v.CnN = 1,  mean_v.CwN = 0, mean_v.CnW=0,
              mean_v.CwW = 1,  mean_v.FnN = 1,  mean_v.FwN=0,
              
              mean_v.FpN = 0, mean_v.FnW = 0,   mean_v.FwW = 1,
              mean_v.FpW = 0 ,  mean_v.fa = 0,  mean_v.FpP = 1,
              
              mean_v.HnN = 1, mean_v.HwN = 0,   mean_v.HpN = 0,
              mean_v.HnW = 0, mean_v.HwW = 1,   mean_v.HpW = 0,
              mean_v.HpP = 1)


prior.p.scale <-c(A = 1, B.C.N = 1,  B.F.N = 1,  B.H.N = 1,
              B.C.W = 1,  B.F.W = 1,  B.H.W = 1,
              B.F.P = 1,  B.H.P = 1,

              t0=.3,

              mean_v.CnN = 2,  mean_v.CwN = 2, mean_v.CnW = 2,
              mean_v.CwW = 2,  mean_v.FnN = 2,  mean_v.FwN = 2,

              mean_v.FpN = 2, mean_v.FnW = 2,   mean_v.FwW = 2,
              mean_v.FpW = 2,  mean_v.fa = 2,  mean_v.FpP = 2,

              mean_v.HnN = 2, mean_v.HwN = 2,   mean_v.HpN = 2,
              mean_v.HnW = 2, mean_v.HwW = 2,   mean_v.HpW = 2,
              mean_v.HpP = 2)

p.prior <- BuildPrior(
  dists = rep("tnorm", 29),
  p1 = prior.p.mean,
  p2 = prior.p.scale,
  lower = c(rep(0, 9), .1, rep(NA, 19)),
  upper = c(rep(NA,9),  1, rep(NA, 19)))

print(p.prior)
```

```{r simulate_subject}
set.seed(1)
dat0 <- simulate(model0, nsim = 1e2, ps = sim.p.vector)
dmi0 <- BuildDMI(dat0, model0)
```


```{r model_fitting_procedure, eval=FALSE}
#
#
# #note ncore argument is useless for single subject fits at the moment
# #just uses 1 core no matter what you input.
# # But will be great when need to dispatch one subject
# #per core
fit0 <- StartNewsamples(dmi0, prior=p.prior,nmc=180, ncore=1, thin=5)
save(fit0, model0, dat0, dmi0, sim.p.vector, p.prior, file = "fit0.RData")
fit  <- run(fit0, thin=5, ncore=1, block=FALSE)
save(fit, fit0, model0, dat0, dmi0, sim.p.vector, p.prior, file = "fit1.RData")
```
